Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-08-20 awipev-CO2.Rmd
adding RMSE on property plots

fit <- lm(data = d_all_at_discrete, at ~ sal_mix)
slope_s_at <- fit$coefficients[[2]]
intercept_s_at <- fit$coefficients[[1]]
at_s <- ggplot(d_all_at_discrete,aes(x=sal_mix, y= at, label = month))+
  geom_text( aes(color=factor(month))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity", y="Discrete AT", color = "Months")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
  theme_bw() +
  theme(aspect.ratio=1,
        axis.text=element_text(size=15),
        axis.title.y= element_text(size =15),
        axis.title.x= element_text(size =15),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70)))

@@

pH is measured continuously by an autonomous seaFET pH sensor. Because of issue, measurement periodicity was set to 1 hour from 2018-02-02 to 2018-04-17. *Note that pH sensor is mounted on a profiling structure. Here, only seaFET data recorded with a depth > 8 m are taken in consideration.* pH calibration is based on monthly discrete samples that are analysed with spectrophotometric method in Villefranche by Samir Alliouane. When it is not possible to sample at the vicinity of the sensor for practice reasons (in winter), sampling is done in the harbour and is not taken in consideration for calibration for spatial reasons.

>>>>

fit <- lm(data = d_all_at_discrete, at ~ sal_mix)
slope_s_at <- fit$coefficients[[2]]
intercept_s_at <- fit$coefficients[[1]]
at_s <- ggplot(d_all_at_discrete,aes(x=sal_mix, y= at, label = month))+
  geom_text( aes(color=factor(month))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity", y="Discrete AT", color = "Months")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
  theme_bw() +
  theme(aspect.ratio=1,
        axis.text=element_text(size=7),
        axis.title.y= element_text(size =7),
        axis.title.x= element_text(size =7),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))

@@

pH is measured continuously by an autonomous seaFET pH sensor. Because of issue, measurement periodicity was set to 1 hour from 2018-02-02 to 2018-04-17. *Note that the pH sensor is mounted on a profiling structure. Here, only seaFET data recorded with a depth > 8 m are taken in consideration.* pH calibration is based on monthly discrete samples that are analysed with spectrophotometric method in Villefranche by Samir Alliouane. When it is not possible to sample at the vicinity of the sensor for practice reasons (in winter), sampling is done in the harbour and is not taken in consideration for calibration for spatial reasons.
